Field-informed Reinforcement Learning of Collective Tasks with Graph Neural Networks

### 2023-08-01 paper.tex
content: on review

  \Cref{fig:static} represents the scenario used during training. 
  The others are used in the test phase to evaluate the policy found. }

>>>>

  \Cref{fig:static} represents the scenario used during training \review{as well as during test}. 
  The others \review{instead} are only used in the test phase to evaluate the policy found. }
